---
title: "Anomaly detector based on PHAD-C32 (1999)"
author: "Francisco Javier Motos Barragán"
date: "July 2018"
output:
  html_document: default
---


```{r setup, include=FALSE,render=FALSE, results='hide',message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE,fig.width=6, fig.height=4)
root.dir <- paste(getwd(),"../../R",sep='/')
source(paste(root.dir,'util/environment.R',sep='/'))
setup(root.dir = root.dir)
library(dplyr)
library(grid)
library(gridExtra)
library(gtable)
library(ggplot2)

print(getDataDir(root.dir))

# Load cached results
conn <- gzfile(paste(getDataDir(root.dir),'cache/testing.measured.ds.cache.RData.gz',sep='/'))
load(conn)
close(conn)
```

This notebook contains the results from evaluating the model aginst the data input. Data is analised in terms of network packets or an attack. An attack represents a group of packets.
The output of the anomlay detector is not a binary result. So, we show results using several thresholds.

# Miminum threshold (scoring less or equal to 1)
### Attack type coverage
In this graph, we can observe how many types of attacks are detected, classified by category.

```{r, Coverage, include=TRUE,render=TRUE, results='hide',message=FALSE}
renderCoverageType(testing.measured.ds, th = 1, TRUE, savetoFile =  FALSE)
```

### Detection by packets and attacktype
Next graph, we show the detection by packets, classified by category.

```{r Detection by attack type, include=TRUE,render=TRUE, results='hide',message=FALSE}
renderAttackTypeDetection(testing.measured.ds, th = 1, TRUE, FALSE)
```

### Detection by attack filtered by category
On this graph, we can see the detection by attack and for specific category. Also we show a table with the Top scored attacks detected (attacks with 0 scored has been removed). 

<div style="float: left; width: 50%;">
```{r Detection by attack filtered by category, include=TRUE,render=TRUE, results='markup',message=FALSE}
renderAttackTypeDetectionDetailed(testing.measured.ds, attackType = 'DOS', th = 1, TRUE, saveToFile = FALSE)
```
</div>
<div style="float: right; width: 50%;">
```{r include=TRUE,render=TRUE, results='markup',message=FALSE}
renderAttackTypeDetectionDetailedTable(testing.measured.ds, attackType = 'DOS', th = 1, TRUE, saveToFile = FALSE)
```
</div>

<div style="float: left; width: 50%;">
```{r include=TRUE,render=TRUE, results='markup',message=FALSE}
renderAttackTypeDetectionDetailed(testing.measured.ds, attackType = 'URA', th = 1, TRUE, saveToFile = FALSE)
```
</div>

<div style="float: right; width: 50%;">
```{r}
renderAttackTypeDetectionDetailedTable(testing.measured.ds, attackType = 'URA', th = 1, TRUE, saveToFile = FALSE)
```
</div>

<div style="float: left; width: 50%;">
```{r}
renderAttackTypeDetectionDetailed(testing.measured.ds, attackType = 'RLA', th = 1, TRUE, saveToFile = FALSE)
```
</div>

<div style="float: right; width: 50%;">
```{r}
renderAttackTypeDetectionDetailedTable(testing.measured.ds, attackType = 'RLA', th = 1, TRUE, saveToFile = FALSE)
```
</div>

<div style="float: left; width: 50%;">

```{r}
renderAttackTypeDetectionDetailed(testing.measured.ds, attackType = 'PRO', th = 1, TRUE, saveToFile = FALSE)
```
</div>

<div style="float: right; width: 50%;">
```{r}
renderAttackTypeDetectionDetailedTable(testing.measured.ds, attackType = 'PRO', th = 1, TRUE, saveToFile = FALSE)
```
</div>

# Analysis with other thresholds

In the next sections we show the same results, but using greater threshold, so the system is less restrictive about waht they consider as an anomaly or an attack.

### False Positives/Negatvives and true detections
Render by package table False Positive/Negative and correct detections with threshold 1 and compare with threshold 20 and 37

* Render by packet, False Positive/Negative and correct detections with threshold 1
```{r Render by package table False Positive/Negative 1, include=TRUE,render=TRUE, results='hide',message=FALSE,fig.width=10, fig.height=2}
renderFPFNTable(testing.measured.ds, threshold = 1, render = TRUE, saveToFile = FALSE)
```

* Render by packet, False Positive/Negative and correct detections comparison between threshold 1 and threshold 20
```{r Render by package table False Positive/Negative 1-20, include=TRUE,render=TRUE, results='hide',message=FALSE,fig.width=10, fig.height=3}
renderFPFNTableComparison(testing.measured.ds,1,20, saveToFile = FALSE)
```

* Render by packet, False Positive/Negative and correct detections comparison between threshold 1 and threshold 20
```{r Render by package table False Positive/Negative 1-37, include=TRUE,render=TRUE, results='hide',message=FALSE,fig.width=10, fig.height=3}
renderFPFNTableComparison(testing.measured.ds,1,37, saveToFile = FALSE)
```

### False Positives/Negatives and true detections (based on number of attacks)
Render by number of attacks table False Positive/Negative and correct detections with threshold 1 and compare with threshold 20 and 37

* Render by attack, False Positive/Negative and correct detections with threshold 1
```{r Render by package table False Positive/Negative 1 attacks, include=TRUE,render=TRUE, results='hide',message=FALSE,fig.width=10, fig.height=2}
renderFPFNByAttackTable(testing.measured.ds,1, render = TRUE, saveToFile = FALSE)
```

* Render by attack, False Positive/Negative and correct detections comparison between threshold 1 and threshold 20
```{r Render by package table False Positive/Negative 2-20 attacks, include=TRUE,render=TRUE, results='hide',message=FALSE,fig.width=10, fig.height=3}
renderFPFNByAttackTableComparison(testing.measured.ds,1,20, saveToFile = FALSE)
```

* Render by attack, False Positive/Negative and correct detections comparison between threshold 1 and threshold 37
```{r Render by package table False Positive/Negative 2-37 attacks, include=TRUE,render=TRUE, results='hide',message=FALSE,fig.width=10, fig.height=3}
renderFPFNByAttackTableComparison(testing.measured.ds,1,37, saveToFile = FALSE)
```
